\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2019-04-29 doc/paper.tex
Update conclusion and discussion section

\section{Conclusion and Discussion}
[Abundance of bad leaders. Coups are still commonplace]

[How we tackle the problem. Strength of our design]

[What our analysis suggest. Summary of findings]

[Compare results to other literature. i.e., magnitude of stock changes. Democratization is not guarantee of positive stock returns]

[Discuss potential mechanisms. Note as a limitation and an avenue for future research.]

This paper has examined the effects of irregular regime changes on financial returns. It uses an event study approach to show that investors expect irregular regime changes to have large effects on equity returns. This methodology is less susceptible to endogeneity biases than studies that use cross country data.

The results are consistent with the idea that perceptions of government competence and changes in government have large impacts on investor confidence. However, we do not find that irregular regime changes universally discourage investment. Instead, financial volatility surrounding regime changes is often characterized by large negative \textit{and} positive stock returns, which suggests that irregular regime changes increase policy uncertainty and volatility, but that uncertainty does not tell the whole story. The direction of returns depends on the type of irregular regime change and its expected outcome. Abnormal returns following resignations are large and positive (4\%), abnormal returns following assassinations are negative and smaller in magnitude (2\%), and abnormal returns following coups also tend to be negative (2\%). However, some coups result in positive abnormal returns of 10\% or more. The variation in the direction of abnormal returns is therefore consistent with the idea that not all types of regime changes are equivalent in terms of expected economic policy outcomes.

Our findings suggest that abnormal returns are likely positive following resignations because those leaders were likely to be ``bad'' leaders, and coups may result in positive returns in the event of a transition to more democratic or pro-business leadership. Conversely, autocratic coups may increase fear of capital appropriation or the institution of poor economic policies, while assassinations may be merely regarded as highly uncertain events. However, while our research design allows us to show that different types of irregular regime changes can be expected to result in different financial outcomes on average, it does not allow us to directly test the mechanisms that result in this variation. We therefore leave more direct tests of these mechanisms to future research.

>>>>

\section{Conclusion and Discussion}
Max Weber (\citeyear{weber1947theory}) developed the concept of ``charismatic leadership'' whereby a leader's authority stems from their charisma. Such rule is often found in autocracies with weak institutions and few constrains placed on the power of leaders. \citet{jones2005leaders} has shown that leaders can have particularly large impacts on economic growth in these settings. It is therefore not surprising that there is often a strong temptation to overthrow "bad" leaders, even by undemocratic means.

Coups and other types of regime changes remain common, highlighting their relevance for economic and political development. Our sample consists of 5 coups, 1 assassination, 7 resignations, and 7 instances of public protect since 2000. The Arab spring is perhaps the most notable, with protests in response to oppressive regimes and low living standards spreading throughout the Middle East in late 2010. There have also been a number of failed coups such as the 2002 coup attempt against Hugo Chavez and the 2016 failed coup in Turkey. Yet despite their frequency there is little evidence on their economic consequences.

This paper helps fill the evidence gap by using an event study approach that exploits daily returns of national stock market indices. This approach provides well-identified estimates of the economic effects of regime changes that are less susceptible to endogeneity bias than prior cross country studies. Furthermore, the large sample of political events in our study increases the generalizability of our findings.

The results are consistent with the idea that perceptions of government competence and changes in government have large impacts on investor confidence. But although the effect of regime changes and protests on stock volatility is substantial, the effect on the direction of stock returns is less certain. Abnormal returns following resignations are large and positive (4\%), abnormal returns following assassinations are negative and smaller in magnitude (2\%), and abnormal returns following coups also tend to be negative (2\%). However, the returns surrounding the failed 2002 coup that temporarily ousted Hugo Chavez from power in Venezuela show that coups can sometimes have large positive economic effects, which is consistent with estimates from \citet{girardi2018institution} showing  the election of Allende in Chile and the subsequent coup replacing him increased stock market valuations. In total, the evidence consequently suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist governments are replaced with more pro-business ones. Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies, while assassinations may be merely regarded as highly uncertain events.

As in any study, there are a number potential avenues for future research. First, more research is needed to identify the pro- and anti-market characteristics of regime changes. These may be the types of regime changes used in this paper or more nuanced characteristics. Ideally, researchers would be better able to predict the expected effects of future regime changes on stock returns. Additionally, it would be useful to identify the mechanisms through which regime changes effect stock returns. In the case of Chile,  \citet{girardi2018institution} shows that increasing stock market valuations were caused by changes in private property rights rather than economic growth prospects or wage costs. Research focusing on the mechanisms in other settings would help generalize these findings. Lastly, it would be helpful to determine the extent to which stock market returns translate to broader economic development outcomes. \citet{meyersson2016political} has made progress on this front by examining the impact of coups on a number of outcomes in addition to economic growth including investment, debt, inflation, infant mortality, and years of schooling. It would be fruitful to examine whether the direction of the effects of different types of regime changes on these outcomes are consistent with their stock market effects. Such research can help enlarge the body of evidence on the extent to which regime changes cause institutional and political change, and, in turn, have significant consequences for economic development.
